---
title: "An introduction to Bayes.Glmm"
author: "Xulong Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An introduction to Bayes.Glmm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this tutorial, we demonstrate how to use Bayes.GLMM in a genome-wide association analysis using ADSP data as an example. In ADSP, whole genome sequences (WGS) results of 576 individuals from 111 families were collected. Each individual was diagnosed with one of the four AD levels: no (80), possible (81), probable (360), and definite (55). Additional sample information includes family pedigree, race, ethnicity, age, sex, and APOE e2/e3/e4 genotypes.

```{r, include = F}

library(rstan)
library(bayes.glmm)

```

## Example

```{r}
data("sample", package = "bayes.glmm")

pheno = data$pheno
geno = data$geno
cov = data$cov
K = data$K
L <- t(chol(K))

# debug - start
model = stan_model("~/GitHub/bayes.glmm/lib/glm.stan")
g0 = rep(0, 576)
data0 = list(N = 576, K = 4, D = 2, cov = cov, L = L, geno = g0, pheno = pheno)
data0$prior_non = 1
data0$prior_inf = 0
optimizing(model, data = data0)

# end - end

model = data$model

config0 = list(chains = 3, iter = 400, warmup = 200, cores = 3)

g0 = rep(0, 576)
data0 = list(N = 576, K = 4, D = 2, cov = cov, L = L, g = g0, pheno = pheno)
data0$prior_non = 1
data0$prior_inf = 0

y = myGWAS_optimizing(model = model, geno = geno[1:5, ], data0)
# y = myGWAS_sampling(model = model, geno = geno[1:5, ], data0, config0)

```
